Analyzing How Organization Size, Sector, and Cybersecurity Strategies Influence Impacts on Cyberattacks

### 2024-04-10 paper/datasheet_template.qmd
Adding datasheet

---
title: "Datasheet for Air quality index by municipality, Leading causes of death
and Average PM2.5 concentrated data dataset"
author: 
  - Vanshika Vanshika
  - Shivank Goel
  - Navya Hooda
thanks: "Code and data are available at: https://github.com/shivankgoel003/Mortality-in-Alberta."
date: "`r Sys.time()`"
date-format: "D MMMM YYYY"
abstract: "This datasheet documents the datasets used in a study analyzing the impact of air pollution on health outcomes in Alberta, Canada. The data for the study is sourced from the Alberta government's open data portal. It spans several years and includes variables like AQHI readings, PM2.5 concentrations, and mortality rates linked to specific health conditions. This dataset is helpful for its concise representation to study the environmental health in Alberta. It offers insights into public health implications of air pollution. The data cleaning and processing done using tools like R, ensures its reliability and accuracy. This datasheet is an essential guide to the dataset's structure, collection process, and potential applications."

@@

The dataset was created to investigate the correlation between air quality, particularly PM2.5 levels, and mortality rates due to respiratory and cardiac illnesses in Alberta. The aim was to understand how air pollution impacts public health in this region.

@@

The datasets were created by the Alberta Government, specifically by Jobs, Economy and Northern Development, Service Alberta, and Environment and Parks departments.

@@

The creation of these datasets was likely funded by the Alberta government. No specific grant details were provided.

@@

These datasets provide critical insights into environmental and public health concerns in Alberta and are vital for ongoing research and policy development in these areas.

@@

The instances represent various types of environmental and public health data. The first dataset details the Air Quality Health Indices by municipality in Alberta. The second dataset provides information on the leading causes of death in Alberta. The third dataset offers data on PM2.5 concentrations in Alberta.

@@

The exact number of instances is not specified, but each dataset covers multiple years of data across various locations in Alberta.

@@

The datasets seem to be comprehensive for their respective scopes, covering broadly geographical areas within Alberta. It seems to be representative of the larger set of environmental and health data within the province.

@@

Each dataset has specific labels or targets. For the air quality index, the labels include AQHI values and municipal regions. The causes of death dataset labels include types of illnesses and mortality counts. The PM2.5 dataset's labels consist of concentration levels, locations, and time periods

@@

Each dataset has specific labels or targets. For the air quality index, the labels include AQHI values and municipal regions. The causes of death dataset labels include types of illnesses and mortality counts. The PM2.5 dataset's labels consist of concentration levels, locations, and time periods.

@@

There is no specific mention of missing information. However, as with most large datasets, there may be gaps due to data unavailability or limitations in data collection.

@@

The datasets do not explicitly mention relationships between individual instances, but they can be inferred. For example, higher AQHI and PM2.5 values may correlate with increased mortality rates from certain diseases.

@@

Specific errors or sources of noise are not mentioned. However, as with any environmental data, there may be variabilities and inconsistencies due to natural fluctuations and measurement limitations.

@@

The datasets are self-contained and available through the Alberta open data portal. They are subject to the Open Government Licence - Alberta, which allows for reuse and distribution.

@@

There is no content in these datasets that would be considered offensive or insulting. The data is factual, focusing on environmental and health statistics.

@@

The datasets do not specify sub-populations like age or gender. They are more focused on geographical and temporal aspects of air quality and health outcomes.

@@

Individual identification is not possible with these datasets as they deal with aggregated data at the municipal level or higher.

@@

The datasets do not contain sensitive personal data. They are focused on environmental measures and aggregated health outcomes.

@@

The data were directly observed and collected through environmental monitoring stations and health records. They are likely verified through standard government data validation processes, though specific details are not provided.

@@

The air quality and PM2.5 data were likely collected using environmental monitoring stations equipped with sensors. The causes of death data were probably compiled from health records.

@@

The datasets seem to be comprehensive collections rather than samples. They likely  represent the entire population of interest (i.e., all municipalities in Alberta for air quality and all recorded causes of death).

@@

Data collection was likely conducted by government employees or contractors. Specific details about their compensation are not provided.

@@

The data collection covers several years, as indicated by the datasets (e.g., 2001-2021 for the leading causes of death).

@@

The data were collected from environmental monitoring stations and health records, not directly from individuals. It is a secondary data source.

@@

The datasets have likely been used for academic research and study before. They have been used to analyze the relationship between mortality rates and causes of certain diseases.

@@

No specific repository is mentioned, but the datasets are available through the Alberta open data portal.

@@

The data could be used for further environmental health studies, public health planning, and educational purposes.

@@

The data should  not be used for identifying or targeting specific individuals.

@@

The datasets are valuable for understanding trends and correlations in environmental and public health. They should be used appropriately, considering their scope and limitations.

@@

The datasets are publicly available and can be accessed by third parties. They are distributed under the Open Government Licence - Alberta, which allows for use and distribution by anyone.

@@

The datasets are available for download through the Alberta open data portal. There is no mention of a DOI or distribution through other platforms like GitHub.

@@

The datasets are already available for public access.

@@

The datasets are distributed under the Open Government Licence - Alberta, which permits a wide range of uses. The license details can be found on the Alberta open data portal.

@@

There are no specified export controls or regulatory restrictions beyond the Open Government Licence - Alberta.

@@

The datasets are maintained by the respective departments of the Alberta government – Jobs, Economy and Northern Development, Service Alberta, and Environment and Parks.

@@

Contact information is likely available through the Alberta government’s open data portal.

@@

The datasets are updated annually. Specific communication channels for updates are not mentioned.

>>>>

---
title: "Datasheet for Dataset of Data Breaches and Ransomware Attacks Over 15 Years"
author: 
  - Shivank Goel
thanks: "Code and data are available at: https://github.com/shivankgoel003/DataBreach_Ransomware_Stat."
date: today
date-format: long
abstract: "This datasheet documents the datasets used in a studying data breaches and ransomware attacks over 15 years, from 2004 to 2019. The dataset in the study  is compiled by researchers Tsen, Elinor, Ko, Ryan, and Slapnicar, Sergeja, and is based on public data.It serves as a great resource for analyzing trends and patterns in organizational cyber resilience. The focus is on the organizational size, industry sector, and impact of cybersecurity strategies, helping us to better understand how businesses deal with digital threats."

@@

The dataset was created to investigate the cybersecurity incidents impacting various organizations, considering their size and sector. It helps to understand the importance of cybersecurity and the need for a strong defense against such threats.

@@

The dataset was compiled by Tsen, Elinor, Ko, Ryan, and Slapnicar, Sergeja, affiliated with The University of Queensland.

@@

The dataset compilation was part of a PhD project, presumably supported by funding allocated for academic research by The University of Queensland. No specific grant number is associated with the dataset creation, as per the available information.

@@

The dataset is a resource for researchers, policymakers, and cybersecurity professionals to study cyber resilience in today's digital world.

@@

The instances within the dataset represent cybersecurity incidents, especially data breaches and ransomware attacks on various organizations. Each instance shows details such as the nature of the attack, the sector and size of the organization affected, the geographical location, and the impact and response measures.

@@

The exact number of cyberattack instances are 1146 of each type withing 15 years of time frame from 2004 to 2020.

@@

The dataset does not cover all possible instances but represents a broad selection from multiple resources. It is a sample of large number of cyber incidents, focusing on publicly reported and confirmed attacks. It includes a diverse range of incidents from various sectors and countries to provide a representative overview of cyber threats.

@@

Each instance includes processed data with features such as the year of the attack, the name of the organization, critical industry classification, organization size, level of digital intensity, the sector, country, details of the cyber security role and frameworks, impact level, and actions taken. This provides a structured understanding of each incident.

@@

Each instance is labeled with the type of attack (e.g., ransomware, data breach) and classified by its impact level (e.g., low, medium, high) based on the response taken by the organization.

@@

There is many missing information in the dataset.This might be due to provacy concerns, or some orgnizations did not report the exact information. For example, instances such as number of users affected has lot of gaps in the dataset.

@@

The datasets do not explicitly mention relationships between individual instances, however they can be drawn while doing statistical analysis.

@@

Specific errors or sources of noise are not mentioned. However, as with any databreach report data, there may be variabilities and inconsistencies due to natural fluctuations and measurement limitations.

@@

The datasets are self-contained and available through the website of University of Queensland.

@@

There is no content in these datasets that would be considered offensive or insulting. The data is factual, focusing on data breaches and cyber incidents.

@@

The datasets do not specify sub-populations like age or gender.

@@

Individual identification is not possible with these datasets as they deal with aggregated data covering various countries.

@@

The datasets do not contain sensitive personal data.

@@

The data were directly observed and collected through various resources such as : Carnegie Mellon’s List of Banking Cyber Incidents (2020), Repository of Industrial Security Incidents (2015), Privacy Rights ClearingHouse (2020) and Information is Beautiful (2020).

@@

Not applicable since the dataset was compiled from various resources.

@@

The datasets seem to be collections rather than samples.

@@

Not applicable, since the dataset was compliation of data from other resouces related to cyber atatcks and cyber security.

@@

The data collection covers several years, as indicated by the datasets (e.g., 2004-2020 for the data breach incidents).

@@

Not applicable

@@

	The dataset has been used in academic studies to analyze and understand cybersecurity incident trends. The author themselves have published an academic paper based on the dataset.

@@

The University of Queensland’s eSpace repository contains links to publications and related datasets. The dataset and related works can be accessed at UQ eSpace.

@@

The data could be used for further statistical analysis in the field of cyber risks and cybersecurity.It may also be used for educational purposes, to train machine learning models, or for benchmarking organizational cybersecurity practices.

@@

The dataset should not be used for tasks that could compromise the privacy or security of the affected organizations.

@@

The datasets are valuable for understanding trends and correlations in cyber incidents. They should be used appropriately, considering their scope and limitations.

@@

The dataset is already in the public domain and is available to third parties for research and analysis. It can be accessed globally, subject to the terms of use set by the University of Queensland.

@@

The dataset is distributed online through the University of Queensland's data collection portal. It does have a DOI, which can be used to cite the dataset in academic work.

@@

The dataset is already available and has been since its publication year in 2020.

@@

Yes, the dataset is distributed under a license that permits reuse with acknowledgment, and the terms are outlined in the dataset’s access conditions on the University of Queensland’s website.

@@

There are no export controls or regulatory restrictions mentioned for this dataset.

@@

The dataset will continue to be hosted and maintained by the University of Queensland, ensuring its accessibility for ongoing and future research.

@@

Enquiries about the dataset can be directed to the corresponding author of the research or the data management team at the University of Queensland. Contact can typically be made through the contact details provided on the dataset's webpage.

@@

Updates to the dataset, if any, will be managed by the research team at the University of Queensland. They would be responsible for correcting any errors, adding new data, or removing outdated instances.

### 2024-04-10 paper/paper.qmd
Adding datasheet

---
title: "Analyzing How Organization Size, Sector, and Cybersecurity Strategies Influence Impacts on Cyberattacks"
subtitle: "Based on Data Collected From the University of Queensland"
author: 
  - Shivank Goel
thanks: "Code and data are available at: https://github.com/shivankgoel003/DataBreach_Ransomware_Stats"
date: today
date-format: long
abstract: "Undoubtedly as technology is progressing and we are stepping more closer to the digital world, the digital threats are also increasingly rapidly. This studys discusses the influence of organizational size, sector, and cybersecurity strategies on cyberattack impacts. Utilizing a dataset from the University of Queensland about data breaches and ransomware attacks from 2004 to 2019, we analyze the trends and correlations and study how different factors contribute to the severity and frequency of these incidents. Our analysis reveals key insights: larger organizations report more cyber incidents, sectors like healthcare and education are frequent targets, and cybersecurity frameworks significantly help in reducing the user impact. These findings highlight critical areas for how organizations can improve their security and protect their data.
header-includes:
   - \usepackage{tikz}
   - \usetikzlibrary{shapes.geometric, arrows.meta, positioning, fit, calc}
   - \usepackage{pgfplots} 
   - \usepackage{float}
   - \usepackage{booktabs}
   - \usepackage{longtable}

>>>>

---
title: "Analyzing How Organization Size, Sector, and Cybersecurity Strategies Influence Impacts on Cyberattacks"
subtitle: "Based on Data Collected From the University of Queensland"
author: 
  - Shivank Goel
thanks: "Code and data are available at: https://github.com/shivankgoel003/DataBreach_Ransomware_Stats"
date: today
date-format: long
abstract: "Undoubtedly as technology is progressing and we are stepping more closer to the digital world, the digital threats are also increasingly rapidly. This study discusses the influence of organizational size, sector, and cybersecurity strategies on cyberattack impacts. Utilizing a dataset from the University of Queensland about data breaches and ransomware attacks from 2004 to 2019, we analyze the trends and correlations and study how different factors contribute to the severity and frequency of these incidents. Our analysis reveals key insights: larger organizations report more cyber incidents, sectors like healthcare and education are frequent targets, and cybersecurity frameworks significantly help in reducing the user impact. These findings highlight critical areas for how organizations can improve their security and protect their data."
header-includes:
   - \usepackage{tikz}
   - \usetikzlibrary{shapes.geometric, arrows.meta, positioning, fit, calc}
   - \usepackage{pgfplots} 
   - \usepackage{float}
   - \usepackage{booktabs}
   - \usepackage{longtable}
